### 2017-07-09 README.Rmd
fixed typo
added logo
resize logo

# pdp: An R Package for Constructing Partial Dependence Plots

@@

A detailed introduction to `pdp` has been published in The R Journal: "pdp: An R Package for Constructing Partial Dependence Plots", https://journal.r-project.org/archive/2017/RJ-2017-016/index.html. You can track development on  at https://github.com/bgreenwell/pdp. To report bugs or issues, contact the main author directly or submit them to https://github.com/bgreenwell/pdp/issues.

>>>>

# pdp: An R Package for Constructing Partial Dependence Plots <img src="tools/pdp-logo.png" align="right" width="120" height="139" />

@@

A detailed introduction to `pdp` has been published in The R Journal: "pdp: An R Package for Constructing Partial Dependence Plots", https://journal.r-project.org/archive/2017/RJ-2017-016/index.html. You can track development at https://github.com/bgreenwell/pdp. To report bugs or issues, contact the main author directly or submit them to https://github.com/bgreenwell/pdp/issues.
